---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# adfgcolors

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->


This package allows users to easily add common ADF&amp;G colors schemes in ggplot2

Inspired by the amazing packages [nmfspalette](https://github.com/nmfs-general-modeling-tools/nmfspalette) and [PNWColors](https://github.com/jakelawlor/PNWColors). Much of the code from this package is from nmfspalette, written by [Christine Stawitz](https://github.com/ChristineStawitz-NOAA).


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("justinpriest/adfgcolors")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(adfgcolors)
## basic example code
```


## Palette Choices
Colors are generally divided into two categories, discrete and continuous. Palettes are able to be used as either type, though generally the palettes described below as discrete display best when plotted for discrete data.

### Continuous (Sequential) Palettes
```{r colordemos_cont, fig.height=2, echo = FALSE}
display_palette("glacier", 7)
display_palette("sitkasunset", 7)
display_palette("aurora", 7)
display_palette("rockfish", 7)
display_palette("blues", 7)
display_palette("blues2", 7)
display_palette("grays", 7)
display_palette("grays_bw", 7)


```

### Discrete (Categorical) Palettes
```{r colordemos_disc, fig.height=2.25, echo = FALSE}
display_palette("totem", 5)
display_palette("logo", 6)
display_palette("tetrad", 4)
display_palette("discrete7", 7)


```


