---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# adfgcolors

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

<!-- badges: end -->

This package allows users to easily add useful and aesthetic colors schemes in ggplot2. Influenced by the amazing packages [nmfspalette](https://github.com/nmfs-general-modeling-tools/nmfspalette) and [PNWColors](https://github.com/jakelawlor/PNWColors). Much of the code for this package is from nmfspalette, written by [Christine Stawitz](https://github.com/ChristineStawitz-NOAA).

adfgcolors is still in active development with new palettes being added. adfgcolors is not endorsed by ADF&G.  


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("justinpriest/adfgcolors")
```
## Example Usage

adfgcolors allows you to quickly specify color palettes in ggplot by using the functions `scale_fill_adfg()` and `scale_color_adfg()`, shown below:  
```{r demoplotglacier, fig.height=3}
library(adfgcolors)
library(ggplot2)
ggplot(mpg, aes(class, fill = class)) +
  geom_bar(color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_adfg(palette = "glacier", discrete = TRUE) 

```

A common need is for plots to be in grayscale, shown here:
```{r demoplotgray, fig.height=3}
library(adfgcolors)
library(ggplot2)
ggplot(mpg, aes(class, fill = class)) +
  geom_bar(color = "black") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_adfg(palette = "grays_bw", discrete = TRUE) 
```

The color aesthetic is easy to modify:
```{r demoplotcolor, fig.height=3}
library(adfgcolors)
library(ggplot2)
ggplot(mpg, aes(x=displ, y = cty, color = cyl)) +
  geom_point() + 
  scale_color_adfg(palette = "aurora", discrete = FALSE) 

```

Often, discrete variable plots look best if the exact order of colors are used (no interpolation):
```{r demoplotexact, fig.height=3}
library(adfgcolors)
library(ggplot2)
ggplot(mpg, aes(drv, fill = drv)) +
  geom_bar(color = "black") + 
  scale_fill_adfg(palette = "bristolbay", discrete = TRUE, useexact = TRUE) 
```


<br>  

## Palette Choices
Colors are generally divided into two categories, discrete and continuous. Palettes are able to be used as either type, though palettes described below as discrete display best when plotted for discrete data. Palettes are shown with hex codes for use in manual plotting, if desired. To show palettes, use function `display_palette()`.

### Continuous (Sequential) Palettes
```{r colordemos_cont, fig.height = 2, echo = FALSE}
pallistcont <- c("glacier", "sitkasunset", "aurora", "grays_bw")
# excluding "blues"

for(j in 1:length(pallistcont)){
  display_palette(pallistcont[j], 7)
}

```

<br>  
 
### Discrete (Categorical) Palettes 
_Consider using argument_ `useexact = TRUE` _when plotting discrete variables as it will use the exact order of palettes shown below._
```{r colordemos_disc, fig.height=2.25, echo = FALSE}
pallistdisc <- c("totem", "logo",  "bristolbay", "discrete7")
optlen <- c(5, 6, 7, 7)

for(j in 1:length(pallistdisc)){
  display_palette(pallistdisc[j], optlen[j])
}

```

### Other Palettes  
**More continuous palettes**   
```{r otherpalettescont, fig.height=1.25, echo = FALSE}

display_palette_small <- function(name, n, ...) {
  pal <- adfg_paletter(name)(n)

  old <- par(mar = c(0.25, 0.25, 0.25, 0.25))
  on.exit(par(old))

  image(1:n, 1, as.matrix(1:n), col = pal,
        xlab = "",
        ylab = "", xaxt = "n",
        yaxt = "n", bty = "n", ...)

  rect(0, 0.8, n + 1, 1, col = rgb(1, 1, 1, 0.8), border = NA) # opaque rect
  text((n + 1) / 2, 0.9, labels = paste(name), cex = 1, family = "sans", col = "#32373D") # palette name
  #rect(0, 0.6, n + 1, 0.8, col = rgb(1, 1, 1, 1), border = NA) # white bottom fill
  rect(0.5, 0.6, n +0.5, 1.4, col = rgb(1, 1, 1, 0), border = "#000000") # black border #0.5, 0.8,
}

par(mfrow=c(1,2))

display_palette_small("rockfish", 7)
display_palette_small("blues2", 7)

display_palette_small("grays", 7)
display_palette_small("tongass", 7) 
```

**More discrete palettes**
```{r otherpalettesdisc, fig.height=1.25, echo = FALSE}
par(mfrow=c(1,2))
display_palette_small("berries", 5)
display_palette_small("coho", 6)

display_palette_small("denali", 7)
display_palette_small("tetrad", 4)

```


